\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-11-19 main.tex
Updates from Overleaf

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.5
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_triangles=8_000, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
solution.plot_fields()
solution.plot_currents()
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
\label{code:device}
\end{code}
Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles). In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.5\,\um$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. c) Current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}.}
    \label{fig:ring-with-slit}
\end{figure*}

>>>>

# Define the device geometry.
length_units = "um"
ro = 3  # outer radius
ri = 1  # inner radius
slit_width = 0.5
Lambda = 1  # effective penetration depth
# circle() and box() generate arrays of polygon (x, y) coordinates.
ring = circle(ro)
hole = circle(ri)
slit = box(slit_width, 1.5 * (ro - ri), center=(0, -(ro + ri) / 2))
# Define the Polygon representing the superconductor.
layer = sc.Layer("base", Lambda=Lambda)
film = sc.Polygon.from_difference(
    [ring, slit, hole], name="ring_with_slit", layer="base"
)
bounding_box = sc.Polygon("bounding_box", layer="base", points=circle(1.2 * ro))
# Create a Device and generate and plot the computational mesh.
device = sc.Device(
    film.name,
    layers=[layer],
    films=[film],
    abstract_regions=[bounding_box],
    length_units=length_units,
)
device.make_mesh(min_triangles=8_000, optimesh_steps=None)
device.plot(mesh=True)
# Calculate the device's response to a uniform applied field.
applied_field = sc.sources.ConstantField(10)
solution = sc.solve(device, applied_field=applied_field, field_units="uT")[-1]
# Visualize the solution.
# Plot the magnetic field evaluated at each layer in the Device.
solution.plot_fields()
# Plot the current density evaluated at each layer in the Device.
solution.plot_currents()
# Plot the field evaluated at any points in space.
solution.plot_field_at_positions(device.points, zs=0.5)
\end{minted}
\captionof{listing}{The typical workflow for a \SuperScreen simulation: 1) Define device geometry and materials properties, 2) generate the computational mesh, 3) solve the model for a given applied field, and 4) visualize the results.}
\label{code:device}
\end{code}
Once the layers, films, holes, and abstract regions have been defined, one can generate the computational mesh by calling \inline{Device.make_mesh()}. The region that is meshed is defined by the convex hull of the union of all polygons in the device. Mesh generation is a two step process. First, an initial Delaunay mesh is created using \inline{meshpy}~\cite{Klockner}, which is a Python interface to Triangle~\cite{Shewchuk1996-va, Shewchuk}, a fast compiled 2D mesh generation tool. Second (and optionally), the mesh is further optimized using \inline{optimesh}~\cite{Schlomer2021-ua}. The goal of the mesh optimization step is to improve the ``quality'' of each triangular element in the mesh, where quality measures how close a triangle is to equilateral (quality $\leq1$, with equality for equilateral triangles). In practice, the more \inline{optimesh} steps are performed, the more uniform in size and spatial density the triangles in the mesh become.
% , where quality is defined as twice the ratio of the incircle radius to the circumcircle radius (quality $\leq1$, with equality for equilateral triangles).
The local density of triangles in the mesh is determined by the density of vertices in the device's polygons and the total number of triangles. Regions where there are many polygon vertices will be meshed more densely than regions with few polygon vertices. If no \inline{optimesh} optimization is done, then every polygon vertex is guaranteed to be a mesh vertex. See Code Block~\ref{code:device} for a demonstration of the process of creating a \inline{Device}, and Figure~\ref{fig:ring-with-slit}(a) to view the resulting geometry and mesh. After the mesh has been generated, the geometry-dependent matrices and vectors described in Section~\ref{section:implementation} are computed and one can begin solving models.

\subsection{Solvers}
\label{section:overview:solvers}
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{examples/images/ring_with_slit.pdf}
    \caption{The output of Code Block~\ref{code:device}: Meissner screening of a uniform $10\,\mu\mathrm{T}$ out-of-plane field by a ring with inner diameter $1\,\um$, outer diameter $3\,\um$, and effective penetration depth $\Lambda=1\,\um$, interrupted by a slit of width $0.5\,\um$. a) Plot of the boundary of the ring (blue), circular bounding box (orange), and the computational mesh (gray), generated with \inline{Device.plot()}. b) The current density $\vec{J}$ in the ring, generated with \inline{Solution.plot_currents()}. c) The $z$-component of the magnetic field $\mu_0H_z$ evaluated at the plane of the ring, generated with \inline{Solution.plot_fields()}. d) The $z$-component of the magnetic field evaluated $z=0.5\,\um$ above the ring (generated using \inline{Solution.plot_field_at_positions()}.}
    \label{fig:ring-with-slit}
\end{figure*}
